\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in, top=0.4in, right=0.4in, bottom=0.4in]{geometry} % Document margins
\usepackage{hyperref} % For clickable links
\usepackage{fontawesome} % For icons
\usepackage{enumitem} % For customizing lists
\usepackage{titlesec} % For customizing section titles

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{\LARGE \textbf{Shubham Murtadak}} % Your name
\address{\LARGE \textbf{AI ML Engineer}} % Your position
\address{\faPhone \hspace{\0.2cm}+91-9322191338 \hspace{1.5cm}  \faEnvelope \hspace{\0.2cm}shubhammurtadak011@gmail.com \hspace{1.5cm} \faLinkedin \hspace{\0.1cm} \href{https://linkedin.com/in/shubham-murtadak}{linkedin} \hspace{1.5cm} \faGithub \hspace{\0.1cm} \href{https://github.com/shubham-murtadak}{github}}

\titleformat{\section}{\LARGE\bfseries}{}{0em}{}[\titlerule] % Customize section titles


\begin{document}





% Your resume content here



\vspace{-7mm}
\hrulefill
\vspace{2mm}


%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{About Me }

{Entry-level Data Scientist with proficiency in Python and Statistics, eager to make a meaningful impact through contribution. I'm passionate, energetic, and geeky individual whose desire to learn is endless. }


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{tabular}{@{} l >{\raggedleft\arraybackslash}p{0.5\linewidth}@{}}
\textbf{B.E. in Artificial Intelligence \& Data Science} & \textbf{2021-2025} \\
PES Modern College of Engineering & \\
CGPA: \textbf{9.09}& \\[6pt]

\textbf{Senior Secondary (XII), Science} & \textbf{2020}\\
Shree Ganesh Jr College, HSC Board & \\
Grades: \textbf{83.38\%} & \\[6pt]

\textbf{Secondary (X)} & \textbf{2018} \\
New English School Korhale, India & \\
Grades: \textbf{89\%} & \\
\end{tabular}

\end{rSection}



%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\textbf{Primary Skills:}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, R, C++, SQL
    \item \textbf{Python/ML/CV Packages:} Keras, OpenCV, Pandas, Scikit-Learn, Numpy, Matplotlib, Seaborn, Plotly
    \item \textbf{Knowledge of Machine Learning}
    \item \textbf{Deep Learning:} Neural Network, ANN, CNN, DNN, Transfer Learning, Back Propagation, TensorFlow
    \item Text understanding, representation \& classification techniques, Text clustering
    \item \textbf{Libraries:} BOW, TFIDF, word2vec, doc2vec, sent2vec, keyphrase extraction
    \item LSTM RNN, Transformers
    \item Generative AI, Large Language Models, LangChain Framework  
    \item Statistics, Linear Algebra, Probability
    \item DSA, Problem Solving
\end{itemize}

\textbf{Secondary Skills:}
\begin{itemize}
    \item \textbf{WEB TECHNOLOGIES:} HTML, CSS, JavaScript, Django, Flask, Streamlit
    \item \textbf{DATABASES:} MySQL, MongoDB
    \item \textbf{Visualization Tools:} PowerBI, Microsoft Excel
    \item \textbf{Web Scraping:} Scrapy, BeautifulSoup, Selenium
    \item \textbf{Cloud Platform Services:} AWS
\end{itemize}

\end{itemize}

\end{itemize}



\end{itemize}
\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}
\textbf{Data Science Intern} \hfill May 2024 - present\\
DataNnovite Solutions LLP \hfill \textit{Pune, Maharashtra (Onsite)}
\begin{itemize}[leftmargin=0.5in]
    \itemsep -3pt {}
    \item Working on Data Science technologies including Machine Learning, Deep Learning, Large Language Models, Generative AI.
    \item Performed data preparation to generate insights for the RAG model.
    \item Developed a solution for analyzing and processing clients' transaction and campaign data to feed into a RAG model, enabling the retrieval of answers to specific business questions via a dashboard.
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}

\textbf{1. Automated Business Insights and Campaign Optimization}
\begin{itemize}[leftmargin=0.5in]
    \item Developed a solution for analyzing and processing clients' transaction and campaign data to feed into a RAG model.
    \item Enabled the client to retrieve answers to specific business questions via a dashboard, enhancing decision-making.
    \item Utilized K-means clustering to categorize customers into six segments (e.g., Champion, Potential Loyal).
    \item Predicted customers' next purchases based on historical data.
    \item Generated campaign text messages for customers.
    \item Targeted customers for future campaigns by sending generated text messages via LLM.
    \item \textbf{Tech Stack:}  Python \textbar{} Pandas \textbar{} Numpy \textbar{} LLM (Mixtral-8x7b, Gemini-1.5-Pro) \textbar{} LangChain\end{itemize}
\vspace{4mm}

\textbf{2. D-predicto}
\begin{itemize}[leftmargin=0.5in]
    \item Developed an end-to-end application predicting diabetes, heart disease (82% accuracy), and Parkinson's disease (87% accuracy) using SVM and Logistic Regression models.
    \item Integrated an NLP-driven chatbot into the website to improve user interaction and access to information.
    \item Included a feature for users to book appointments with doctors if needed.
    \item \textbf{Tech Stack:} Python \textbar{} SK Learn \textbar{} ML \textbar{} Numpy \textbar{} Pandas \textbar{} NLP \textbar{} Flask \textbar{} GitHub
\end{itemize}
\vspace{4mm}

\textbf{3. GestureFlow}
\begin{itemize}[leftmargin=0.5in]
    \item Innovatively utilized Computer Vision and Gesture Recognition to redefine presentation interaction by creating a dynamic, hands-free platform for slide navigation and annotation.
    \item {\textbf{Tech Stack:}} Python \textbar{} OpenCV \textbar{} cvzone \textbar{} OS Module \textbar{} Numpy \textbar{} Hand Tracking Module
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Certificates} 
\begin{itemize}[leftmargin=0.5in]
    \item Quatium Data Analytics
    \item Cognizant Artificial Intelligence
    \item Google Cloud Jam 
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements} 
\begin{itemize}[leftmargin=0.5in]
    \item Winners Of Prostart 2023 \textasciitilde Team Matrix First Rank In College 
    \item Academic topper throughout the graduation
    \item Earned Golden Badge in Python On HackerRank 
    \item Solved over 300+ problems across diverse platforms  
\end{itemize}
\end{rSection}

\end{document}
